Figures

### 2019-06-21 figures/07_model-selection.Rmd
separate plots

```{r tn_re}
# map significant random effects hu4s
gg_hu4 <- ggplot() +
    geom_sf(data = hu4) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))

# dotplot tn hu4 randome effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)

plot_grid(gg_hu4, gg_tn_re)
```

>>>>

```{r tn_re_hu4}

# map significant random effects hu4s
gg_hu4 <- ggplot() +
    geom_sf(data = hu4) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))

gg_hu4
```

```{r tn_re}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)

gg_tn_re
```
